---
title: "demixpca R package Using Instruction"
author: "Jinhuan Ke, Nianlin Chen, Zequn Chen"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Package Introduction

### Install the Package

```{r library, message=FALSE, warning=FALSE, include=TRUE}
library(devtools)
devtools::install_github("jhgoblue/demixpca")
library(demixpca)
```
### Use the demixpca Package

The `demixpca` package contains a data simulation function `dpca_data_sim()` for user to simulate data to be used.
Also, the `plot=TRUE` and `plot_margin` allows user to plot the demixed principle components on certain task parameter.
We here firstly simulate an array with shape (200, 4, 50) which means 50 sample neurons, 200 time parameters and 4 stimulus parameters. (Consistent with `label="ts"`).
And plot the first demixed principle component on the stimulus task parameter margin.
```{r warning=FALSE}
R = demixpca::dpca_data_sim(N=50, n_samples=10, pars_lst = c(200, 4), save = FALSE)
res = demixpca::dpca_fit_transform(R, label = 'ts', plot=TRUE, plot_margin = 't')
res = demixpca::dpca_fit_transform(R, label = 'ts', plot=TRUE, plot_margin = 's')
res = demixpca::dpca_fit_transform(R, label = 'ts', plot=TRUE, plot_margin = 'mix')



res = demixpca::dpca_fit_transform(R, label = 'ts', plot=TRUE, plot_margin = 't', regularizer = 0.01)
res = demixpca::dpca_fit_transform(R, label = 'ts', plot=TRUE, plot_margin = 's', regularizer = 0.01)
```

Here is another example.
We simulate an array with shape (3, 200, 4, 50) which means 50 sample neurons, 3 decisions, 200 time points, and 4 stimulus. (Consistent with `label="dts"`).
And plot the first demixed principle component on the decision task parameter margin.

```{r warning=FALSE}
R = demixpca::dpca_data_sim(pars_lst = c(3, 200, 4), save = FALSE)
res = demixpca::dpca_fit_transform(R, label = 'dts', plot=TRUE, plot_margin = 't')
res = demixpca::dpca_fit_transform(R, label = 'dts', plot=TRUE, plot_margin = 's')
res = demixpca::dpca_fit_transform(R, label = 'dts', plot=TRUE, plot_margin = 'd')

res = demixpca::dpca_fit_transform(R, label = 'dts', plot=TRUE, plot_margin = 't', regularizer = 0.01)
res = demixpca::dpca_fit_transform(R, label = 'dts', plot=TRUE, plot_margin = 's', regularizer = 0.01)
res = demixpca::dpca_fit_transform(R, label = 'dts', plot=TRUE, plot_margin = 'd', regularizer = 0.01)
```


```{r warning=FALSE}
R = demixpca::dpca_data_sim(pars_lst = c(3, 200, 4), save = FALSE)
res = demixpca::dpca_fit_transform(R, label = 'dts', plot=TRUE, plot_margin = 't', method = 'svd')
res = demixpca::dpca_fit_transform(R, label = 'dts', plot=TRUE, plot_margin = 's', method = 'svd')
res = demixpca::dpca_fit_transform(R, label = 'dts', plot=TRUE, plot_margin = 'd', method = 'svd')

res = demixpca::dpca_fit_transform(R, label = 'dts', plot=TRUE, plot_margin = 't', regularizer = 0.01, method = 'svd')
res = demixpca::dpca_fit_transform(R, label = 'dts', plot=TRUE, plot_margin = 's', regularizer = 0.01, method = 'svd')
res = demixpca::dpca_fit_transform(R, label = 'dts', plot=TRUE, plot_margin = 'd', regularizer = 0.01, method = 'svd')
```

```{r warning=FALSE}
R = demixpca::dpca_data_sim(pars_lst = c(3, 200, 4), save = FALSE)
res = demixpca::dpca_fit_transform(R, label = 'dts', plot=TRUE, plot_margin = 't', method = 'qr')
res = demixpca::dpca_fit_transform(R, label = 'dts', plot=TRUE, plot_margin = 's', method = 'qr')
res = demixpca::dpca_fit_transform(R, label = 'dts', plot=TRUE, plot_margin = 'd', method = 'qr')

res = demixpca::dpca_fit_transform(R, label = 'dts', plot=TRUE, plot_margin = 't', regularizer = 0.01, method = 'qr')
res = demixpca::dpca_fit_transform(R, label = 'dts', plot=TRUE, plot_margin = 's', regularizer = 0.01, method = 'qr')
res = demixpca::dpca_fit_transform(R, label = 'dts', plot=TRUE, plot_margin = 'd', regularizer = 0.01, method = 'qr')
```



We encourage user to try different dimension, regularization, decomposition method, and return the list of matrices to plot when analyzing higher dimension.


```{r}

R = demixpca::dpca_data_sim(N=800, pars_lst = c(2, 100, 3), save = FALSE)
start_time <- Sys.time()
res = demixpca::dpca_fit_transform(R, n_components=2, label = 'dts', method='rsvd')
print(Sys.time() - start_time)

start_time <- Sys.time()
res = demixpca::dpca_fit_transform(R, n_components=2, label = 'dts', method='svd')
print(Sys.time() - start_time)

start_time <- Sys.time()
res = demixpca::dpca_fit_transform(R, n_components=2, label = 'dts', method='qr')
print(Sys.time() - start_time)

```

```{r}

R = demixpca::dpca_data_sim(N=100, pars_lst = c(2, 100, 3), save = FALSE)
start_time <- Sys.time()
res = demixpca::dpca_fit_transform(R, n_components=2, label = 'dts', method='rsvd')
print(Sys.time() - start_time)

start_time <- Sys.time()
res = demixpca::dpca_fit_transform(R, n_components=2, label = 'dts', method='svd')
print(Sys.time() - start_time)

start_time <- Sys.time()
res = demixpca::dpca_fit_transform(R, n_components=2, label = 'dts', method='qr')
print(Sys.time() - start_time)

```

```{r}

R = demixpca::dpca_data_sim(N=100, pars_lst = c(4, 500, 6), save = FALSE)
start_time <- Sys.time()
res = demixpca::dpca_fit_transform(R, n_components=2, label = 'dts', method='rsvd')
print(Sys.time() - start_time)

start_time <- Sys.time()
res = demixpca::dpca_fit_transform(R, n_components=2, label = 'dts', method='svd')
print(Sys.time() - start_time)

start_time <- Sys.time()
res = demixpca::dpca_fit_transform(R, n_components=2, label = 'dts', method='qr')
print(Sys.time() - start_time)

```


### Reference

Demixed principal component analysis of neural population data   

eLife 2016, https://elifesciences.org/content/5/e10989

